\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{orange}
\usepackage[scale=.93]{geometry}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{verbatim}
\pagestyle{fancy}
\cfoot{\thepage\ of \pageref{LastPage}}

\name{Jennifer Quay}{Minnich}
\address{Miami, Florida. Works remote, EST}
\phone{347-844-1684}
\social[linkedin]{jennifer-quay-minnich}
\email{quay@quay-cncpts.com}
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

\begin{document}
\makecvtitle

\noindent
\textbf{Clearance \& Credentials:} United States Citizen \$\cdot\$ Public Trust Clearance \$\cdot\$ 9+ yrs of Software Engineering

\noindent
\textbf{Education:} B.S., M.S. in Computer Science (Machine Learning focus)
\vspace{4pt}

\section{Technical Proficiency}
\noindent
\textbf{Programming:} Python $\cdot$ SQL $\cdot$ Bash/Shell
\newline \noindent
\textbf{ML Frameworks:} PyTorch $\cdot$ TensorFlow $\cdot$ Scikit-learn $\cdot$ XGBoost $\cdot$ Hugging Face $\cdot$ PEFT $\cdot$ LoRA
\newline \noindent
\textbf{ML \& Data Science:} Neural Networks $\cdot$ Model Evaluation $\cdot$ ETL $\cdot$ Data Governance $\cdot$ Data Cleansing $\cdot$ Feature Engineering $\cdot$ Statistical Modeling $\cdot$ Training + Fine Tuning
\newline \noindent
\textbf{LLMs:} OpenAI $\cdot$ Claude $\cdot$ Gemini $\cdot$ Llama $\cdot$ Prompt Engineering $\cdot$ RAG $\cdot$ Agent Workflows $\cdot$ MCP $\cdot$ Endpoint Evaluation
\newline \noindent
\textbf{NLP \& Retrieval:} LangChain $\cdot$ LlamaIndex $\cdot$ FAISS $\cdot$ BERT $\cdot$ Sentence Transformers
\newline \noindent
\textbf{AI:} Agentic Systems $\cdot$  Automation $\cdot$ Governance $\cdot$ Red Team Testing $\cdot$ Model Alignment $\cdot$ Responsible AI
\newline \noindent
\textbf{Cloud \& Infrastructure:} GCP (Vertex AI $\cdot$ BigQuery) $\cdot$ AWS (Lambda $\cdot$ S3 $\cdot$ SageMaker $\cdot$ Bedrock) $\cdot$ Azure (ML Studio $\cdot$ Blob Storage $\cdot$ Functions) $\cdot$ CUDA $\cdot$ Distributed Training
\newline \noindent
\textbf{CI/CD \& MLOps:} Git $\cdot$ GitHub Actions $\cdot$ Docker $\cdot$ Kubernetes $\cdot$ Weights \& Biases $\cdot$ MLflow $\cdot$ Drift Monitoring $\cdot$ Loss Tracking $\cdot$ Model Versioning
\newline \noindent
\textbf{Visualization \& Dashboarding:} Tableau $\cdot$ Power BI $\cdot$ Plotly/Dash $\cdot$ Matplotlib $\cdot$ Seaborn $\cdot$ Grafana

\section{Publication}
\cventry{2026}{Minnich, Jennifer, Q. (co-author)}{"Stream Recursion Model: A Novel LLM Architecture"}{\newline Submitted to ICML 2026. Research funded by Sandia National Labs (DOE). Under review.}{}{}{}

\section{Experience}
\vspace{4pt}
\cventry{Nov 2024 - present}{ML/AI Engineer, Data Scientist III}{Arch Systems Inc.}{Baltimore, MD (Remote) | Federal contractor | Public Trust Clearance}{}{
\begin{itemize}
    \item Designed crosswalk normalization layer consolidating 15 disparate software inventory sources into normalized PostgreSQL schema (42 tables, 10 views), enabling compliance gap analysis and cost savings identification across DHS.
    \item Developed model-agnostic SOP generator (JENNY) reducing LLM token costs by 88\% through split-phase architecture: LLM handles text extraction, Python handles template mutation with 82-84 validation gates per document, 100\% structural compliance.
    \item Produced enterprise governance analytics from consolidated TRM database, identifying \$9M+ in combined savings across contract optimization and cloud idle resources for DHS.
    \item Built cross-model security evaluation framework comparing OpenAI and Anthropic architectures, producing testing playbooks covering endpoint testing, persona validation, and jailbreak evaluation.
    \item Built Zendesk automation system routing 150 monthly helpdesk tickets across 7 categories using macros, triggers, and webhooks with AI assistant architecture for escalation.
    \item Evaluated enterprise AI platform viability across 100 pilot users for HHS-ACF, building automated pipeline processing millions of logs into Tableau dashboard with user behavior clustering and model utilization analysis.
    \item Architected AI Constitution Testing framework implementing 15+ testing strategies including constitutional AI alignment, red team datasets, and reusable evaluation templates for ACF child welfare policy compliance.
\end{itemize}
}

\vspace{4pt}
\cventry{Jan 2021 - Nov 2024}{Machine Learning Engineer}{ICASA}{Socorro, NM (Remote) | Federal contractor for DOE, State Contractor for NM State Higher Education, NM Legislative Committee | Public Trust Clearance}{}{
\begin{itemize}
    \item Co-authored novel LLM architecture (SRM) achieving GPT-2 performance at half the parameters by introducing learnable inter-stream communication, enabling scalable mechanistic interpretability. Submitted to ICML 2026, funded by Sandia National Labs/DOE.
    \item Built transformer-based NLP pipeline (DistilBERT, BERTopic, KeyBERT) analyzing 5k open-ended survey responses on food and housing insecurity, deployed as Kubernetes-hosted Dash dashboard.
    \item Fine-tuned Llama 2 for natural language to SQL generation against 14 years of state tax data, achieving 95\% query accuracy across three benchmarked approaches (fine-tuned LLM, LangChain, LlamaIndex).
    \item Secured \$1M state funding for healthcare workforce dashboard, building scalable Python data pipeline and Scikit-learn/XGBoost forecasting models predicting coverage gaps.
    \item Delivered ML training series to cross-functional teams covering end-to-end AI workflows from data preparation through model deployment, accelerating internal adoption of ML tooling.
\end{itemize}
}

\vspace{4pt}
\cventry{Feb 2020 - Jan 2021}{Software Engineer, Data Scientist}{Office of Institutional Research, NM Tech}{Socorro, NM (Remote) | NM State Higher Education contract}{}{
\begin{itemize}
    \item Built scalable ETL pipeline consolidating institutional datasets from multiple sources into unified reporting infrastructure used for research funding decisions.
    \item Fine-tuned NLP models for text classification, NER, and sentiment analysis, automating categorization of institutional survey and program data.
    \item Developed student reporting dashboards using Python (Pandas, Matplotlib, Seaborn) with statistical analysis (descriptive, regression, correlative) informing enrollment and funding strategy.
\end{itemize}
}

\vspace{4pt}
\cventry{Apr 2017 - Feb 2020}{Software Engineer, Data Scientist}{Consumer 51}{Philadelphia, PA (Remote) | International e-commerce and consumer technology consultant}{}{
\begin{itemize}
    \item Shipped full-stack web applications (Python, JavaScript) for enterprise e-commerce clients across international markets.
    \item Automated data pipelines and built interactive Tableau dashboards tracking consumer behavior and sales analytics.
    \item Engineered algorithmic trading toolkit integrating Robinhood API, federal economic data feeds, and backtesting engine.
\end{itemize}
}

\vspace{4pt}
\cventry{Jan 2017 - present}{Founder, Principal Consultant}{Quay Concepts}{Remote}{}{
\begin{itemize}
    \item Founded consulting practice specializing in making advanced analytics accessible to nontechnical stakeholders.
    \item Translated complex analytics and ML systems into stakeholder-ready deliverables through consulting engagements, mentorships, and trainings.
\end{itemize}
}

\section{Notable Projects}
\vspace{2pt}
\subsection{Data/AI Implementations - Federal Government}
\cventry{2026}{DHS - USCIS TRM Enterprise Software \& Cloud Governance Analytics}{}{}{}{
    \begin{itemize}
        \item Produced enterprise governance analytics identifying \$9M+ in combined savings across contract optimization (\$7.5M) and cloud idle resources (\$1.5M) for DHS.
        \item Demonstrated TRM value through OCR category analysis: 144 fragmented product names across 6 sources mapping to 2 DHS TRM records, revealing ungoverned spend and redundant AI acquisitions.
        \item Cross-referenced AI use case registry against active contracts, surfacing retired-status products with active spend.
        \item Built endpoint consolidation analysis quantifying cost of multi-tool inventory conflicts across 143 products, making the business case for a single authoritative source and eliminating data reconciliation across three scanning platforms.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{DHS - USCIS TRM Pipeline \& Data Governance Standardization}{}{}{}{
    \begin{itemize}
        \item Built USCIS Technical Reference Model (TRM) from scratch, consolidating \textasciitilde{}15 disparate data systems into a normalized PostgreSQL database via ETL pipeline using APIs, scripts, and manual extracts.
        \item Developed universal data dictionary standardizing cross-system terminology and schema across all consolidated sources.
        \item Standardized adjudication policy for AI/ML software requests within TRM framework.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{DHS - FEMA FIWA SOP Generator (JENNY)}{}{}{}{
    \begin{itemize}
        \item Developed AI-powered SOP generation tool automating the creation of compliant Standard Operating Procedures from agency templates, unstructured text, and written instructions.
        \item Designed hybrid pipeline architecture limiting LLM usage to text extraction with human-in-the-loop review and Python-based template execution, reducing token costs by 88\% compared to monolithic LLM generation.
        \item Benchmarked pipeline across multiple LLMs evaluating cost, latency, and accuracy to identify optimal model configuration.
        \item Validated 100\% structural compliance against agency SOP templates with PII redaction.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{DHS - USCIS Internal Chatbot Security Evaluation}{}{}{}{
    \begin{itemize}
        \item Compared OpenAI and Anthropic architectures on performance, security, and mission fit for internal chatbot deployment.
        \item Produced testing playbook covering endpoint testing, persona validation, workspace security labels, and jailbreak evaluation.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{DHS - FEMA Ops Brief Generator}{}{}{}{
    \begin{itemize}
        \item Automated weekly FEMA operational brief generation by building Python pipeline combining PDF class schedules, Excel Board workbook, and In-Processing schedule data from three source systems.
        \item Eliminated manual data compilation for operational reporting, standardizing field mapping across disparate source formats.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{ACF - OHS IT-AMS Helpdesk Automation}{}{}{}{
    \begin{itemize}
        \item Built Zendesk automation system routing 150 monthly tickets across 7 categories using macros, triggers, and webhooks.
        \item Automated live dashboards and ticket reporting for external teams and stakeholders.
    \end{itemize}
}
\vspace{6pt}
\cventry{2026}{ACF - OHS IT-AMS Data/AI Strategy}{}{}{}{
    \begin{itemize}
        \item Developed current-to-future state strategy and executive presentation for IT-AMS system modernization with ML and AI integration.
        \item Presented implementation roadmap to executive leadership for transitioning legacy system to AI-enabled infrastructure.
    \end{itemize}
}
\vspace{6pt}
\cventry{2025}{HHS - ACF AI Constitution Testing \& Alignment Framework}{}{}{}{
    \begin{itemize}
        \item Developed comprehensive testing framework evaluating LLM compliance with ACF mission requirements for child and family services.
        \item Conducted technical evaluation of enterprise testing platforms (Promptfoo, Deepeval) with Credal AI integration for HHS-ACF.
        \item Built compliant automated testing pipeline implementing 15+ testing strategies including constitutional AI alignment for ACF policy compliance.
        \item Generated red team test datasets using ACF-specific policy constraints and child safety requirements.
        \item Created reusable evaluation templates enabling rapid deployment across multiple federal use cases, reducing testing cycle time.
    \end{itemize}
}
\vspace{6pt}
\cventry{2025}{ACF - OHS Digital Services Transition}{}{}{}{
    \begin{itemize}
        \item Led data analytics and reporting modernization strategy for ACF legacy IT-AMS system.
        \item Developed predictive analytics pipeline forecasting Head Start program compliance, risk, and funding allocation.
        \item Built FedRAMP-compliant real-time dashboards using Tableau and AWS for executive reporting.
    \end{itemize}
}
\vspace{6pt}
\cventry{2025}{HHS-ACF Credal AI Platform Evaluation \& Usage Analytics}{}{}{}{
    \begin{itemize}
        \item Evaluated enterprise viability of Credal AI across 100 pilot users for ACF under the Chief AI Officer, analyzing volume metrics (DAU/WAU, session duration, API calls) and context patterns (use case mapping, copilot adoption, model utilization across GPT-4o/o1-mini/4o-mini).
        \item Engineered memory-optimized star schema via Tableau Hyper API, automating daily ingestion of millions of Credal AI logs with Python-based validation, cleaning, and statistical analysis pipeline.
        \item Applied user behavior clustering algorithms (k-means, hierarchical) to identify adoption patterns and segment user cohorts by engagement level and use case.
        \item Built automated Tableau dashboard providing executive-level insights for enterprise purchase decision.
    \end{itemize}
}
\vspace{6pt}
\cventry{2025}{HHS-ACF Know Your Customer LLM Service Classification}{}{}{}{
    \begin{itemize}
        \item Evaluated LLM effectiveness for classifying services provided by ACF grantees, benchmarking accuracy and efficiency across models.
        \item Developed strategic scaling approach for automated service classification across ACF's thousands of grantees.
    \end{itemize}
}
\vspace{6pt}

\subsection{FinTech Projects using Machine Learning}
\cventry{2022}{Classification of Malicious Cyber Activity via Machine Learning}{}{}{}{
    \begin{itemize}
        \item Developed feature engineering and encoding strategies, implementing Isolation Forest algorithms to categorize events as routine or anomalous.
        \item Evaluated model performance using Scikit-learn with dimensionality reduction (t-SNE), confusion matrices, and AUC-ROC analysis.
    \end{itemize}
}
\vspace{6pt}
\cventry{2022}{Stock Bought Stock Trading Project}{}{}{}{
    \begin{itemize}
        \item Engineered algorithmic trading toolkit integrating Robinhood API, federal economic data feeds, backtesting engine, and live execution with PyQt GUI.
        \item Applied correlative and predictive statistics to validate and optimize trading strategies.
    \end{itemize}
}
\vspace{6pt}

\subsection{Higher Education \& State Funded Data/AI Projects}
\cventry{2024}{Cyber-Physical Sensing Research}{}{}{}{
    \begin{itemize}
        \item Led cross-functional research teams on multi-modal sensing and unintended sensing detection.
        \item Built cloud-based ML pipeline with Python preprocessing and feature extraction for sensor data.
    \end{itemize}
}
\vspace{6pt}
\cventry{2024}{NM Higher Ed Basic Needs Analysis with NLP}{}{}{}{
    \begin{itemize}
        \item Built transformer-based NLP pipeline (DistilBERT, BERTopic, KeyBERT) analyzing 5k open-ended survey responses on food and housing insecurity.
        \item Deployed as Kubernetes-hosted Dash dashboard with Docker containerization and Helm charts.
        \item Created real-time data exploration visualizations with Plotly and Dash.
    \end{itemize}
}
\vspace{6pt}
\cventry{2024}{NM Higher Ed Student Reporting Dashboard}{}{}{}{
    \begin{itemize}
        \item Analyzed data for thousands of students using Python with statistical methods (descriptive, regression, correlative).
        \item Built visualizations that informed research funding allocation decisions.
    \end{itemize}
}
\vspace{6pt}
\cventry{2023}{Healthcare Workforce Dashboard}{}{}{}{
    \begin{itemize}
        \item \$1M funded project to establish and maintain a state healthcare workforce dashboard.
        \item Designed scalable Python data pipeline ingesting large datasets from multiple sources.
        \item Built ML forecasting models (Scikit-learn, XGBoost) predicting healthcare coverage gaps.
    \end{itemize}
}
\vspace{6pt}

\subsection{Research \& Development}
\cventry{2026}{Stream Recursion Model (SRM): A Novel LLM Architecture}{}{}{}{
    \begin{itemize}
        \item Co-authored novel LLM architecture introducing stream-wise attention for learnable inter-stream communication, achieving GPT-2 performance at half the parameters (68M vs 124M). ICML 2026, funded by Sandia National Labs/DOE.
        \item Analysis revealed hub-like stream routing topology and specialized stream behavior, with top 9 of 32 streams accounting for 50\% of causal impact through ablation studies.
        \item Trained three model variants (SRM-base, SRM-med, SRM-large up to 454M params) on OpenWebText using a single 4xL40s GPU cluster over \textasciitilde{}1000 GPU hours.
    \end{itemize}
}
\vspace{6pt}
\cventry{2023}{Analysis of GitHub Repositories using Neural Networks}{}{}{}{
    \begin{itemize}
        \item Mined GBs of GitHub public user data into JSON format using Python (Pandas, NumPy).
        \item Built and trained TensorFlow neural network models profiling repository users.
        \item Predicted next user activity from repository behavior patterns.
    \end{itemize}
}
\vspace{6pt}
\cventry{2023}{Natural Language Interface for NM Tax Data}{}{}{}{
    \begin{itemize}
        \item Fine-tuned Meta AI Llama 2 using HuggingFace and PyTorch, achieving 95\% accuracy for NL-to-SQL generation.
        \item Implemented LlamaIndex and LangChain for optimized RAG.
        \item Deployed on GCP Vertex AI with MongoDB document store.
    \end{itemize}
}
\vspace{6pt}

\section{References}
\cventry{Jane Yang}{Chief Artificial Intelligence Officer, ACF Tech}{\newline Administration for Children and Families, US Department of Health and Human Services}{}{}{
    \begin{itemize}
        \item jane.yang@acf.hhs.gov
        \item (202) 545-4952
    \end{itemize}
}

\cventry{Justin Hoffman}{Principal AI Data Scientist}{\newline Arch Systems}{}{}{
    \begin{itemize}
        \item jhoffman@archsystemsinc.com
        \item (210) 875-8278
    \end{itemize}
}

\section{Education}
\cventry{2017-2022}{BS, MS Computer Science \& Engineering}{\newline New Mexico Institute of Mining \& Technology}{}{}{
    \begin{itemize}
        \item 5yr accelerated BSCS/MSCS program
        \item Merit based CAHSI S-STEM scholar
        \item Tau Beta Pi Engineering Honors Society
    \end{itemize}
}

\end{document}